Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
itemised as requested

\todo{please eventually itemize next}

1. The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesise a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesise} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
%The safety criteria here must be valid for all possible allowed initial states, and so we
After unwinding the transition system corresponding to the previously synthesised controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

3. The second {\sc verify} stage, {\sc precision}, 
 restores soundness with respect to the plant's precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage.

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.

@@

5. The last {\sc verify} stage, {\sc sampling}, 
ensures that the current sampling rate is large enough by using an 
external checker (\addtodo{add more details here once we have them}).

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with abstraction refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

%\todo{please eventually itemize next}
\begin{enumerate}
\item The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesise a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesise} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
%The safety criteria here must be valid for all possible allowed initial states, and so we
After unwinding the transition system corresponding to the previously synthesised controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

\item The second {\sc verify} stage, {\sc precision}, 
 restores soundness with respect to the plant's precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage.

\item The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.

@@

\item The last {\sc verify} stage, {\sc sampling}, 
ensures that the current sampling rate is large enough by using an 
external checker (\addtodo{add more details here once we have them}).

\end{enumerate}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with abstraction refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
